The Astropy Project

### 2017-11-20 main.tex
moved Perry comment to issue

Affiliated packages are listed on the main \astropy website and advertised to the community through \astropy mailing lists, so becoming an affiliated package is a good way for new and existing packages to gain exposure while at the same time promoting \astropy's high standard for code and documentation quality. This process of listing and promoting affiliated packages is one way in which the \astropy project tries to increase code reuse in the astronomical community.

>>>>

Affiliated packages are listed on the main \astropy website and advertised to the community through \astropy mailing lists, so becoming an affiliated package is a good way for new and existing packages to gain exposure while at the same time promoting \astropy's high standard for code and documentation quality. This process of listing and promoting affiliated packages is one way in which the \astropy project tries to help with \inlinecomment{AG}{Increase?} code reuse in the astronomical community.
